### 2020-02-21 manuscript/ERL_global_C_review.Rmd
changed hypotheses to questions

**Here, we synthesize ForC data to provide a big-picture overview of stand-level carbon cycling of the world’s major forest biomes and how it varies with stand age. We address two broad hypotheses: 
H1. The rate of C cycling generally decreases from tropical to boreal regions (i.e., tropical > temperate > boreal), whereas C stocks show less directional variation.
H2. Both C fluxes and stocks generally increase with stand age, with particularly strong tends in autotrophic C fluxes. 
While components of these hypotheses have been previously addressed (e.g., REFS(Luyssaert et al 2007, Anderson et al 2006, Anderson-Teixeira et al 2013), our analysis represents by far the most comprehensive analysis of C cycling in global forests, and thereby stands to serve as a foundation for improved understanding of global forest C cycling.**

@@

*C stocks and fluxes of mature forests*
	Average C cycles for tropical broadleaf, temperate broadleaf, temperate conifer, and boreal forests $\ge$ 100 years old and with no known major disturbance or significant anthropogenic management are presented in Figures 2-5, and statistics for each biome type are also summarized at: [GitHub URL]. Of the # flux and # stock variables mapped in these diagrams, ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, # fluxes and # stocks in temperate broadleaf forests, #fluxes and # stocks in temperate conifer forests, and fluxes and # stocks in boreal forests. For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets were generally consistent. That is, component fluxes and stocks summed to within 1 std of more inclusive fluxes in all but one instance (in temperate conifer forests, $aboveground woody biomass + foliage biomass > aboveground biomass + 1std$; Fig. 4). **This is based on my quick scan of the figures. Need to add a formal automated test: https://github.com/forc-db/ERL-review/issues/16 **

>>>>

Here, we synthesize ForC data to provide a big-picture overview of stand-level carbon cycling of the world’s major forest biomes and how it varies with stand age. We address two broad questions:

1. How do C cycling vary across the worlds major forest biomes (i.e., tropical, temperate, boreal)?

2. How does C cycling vary with stand age?

While components of these questions have been previously addressed (e.g., REFS(Luyssaert et al 2007, Anderson et al 2006, Anderson-Teixeira et al 2013), our analysis represents by far the most comprehensive analysis of C cycling in global forests, and thereby stands to serve as a foundation for improved understanding of global forest C cycling.

@@

#### C stocks and fluxes of mature forests

Average C cycles for tropical broadleaf, temperate broadleaf, temperate conifer, and boreal forests $\ge$ 100 years old and with no known major disturbance or significant anthropogenic management are presented in Figures 2-5, and statistics for each biome type are also summarized at: [GitHub URL]. Of the # flux and # stock variables mapped in these diagrams, ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, # fluxes and # stocks in temperate broadleaf forests, #fluxes and # stocks in temperate conifer forests, and fluxes and # stocks in boreal forests. For variables with records from $\ge$ 7 distinct geographic areas, these ensemble C budgets were generally consistent. That is, component fluxes and stocks summed to within 1 std of more inclusive fluxes in all but one instance (in temperate conifer forests, $aboveground woody biomass + foliage biomass > aboveground biomass + 1std$; Fig. 4). **This is based on my quick scan of the figures. Need to add a formal automated test: https://github.com/forc-db/ERL-review/issues/16 **
